The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-13 document/ms.tex
updated mass pred table
some words of caution about extrapolation

For comparison, we repeated the analysis of \citet{Burke:2015} and fit a
double power-law occurrence rate to the short-period \kepler\ planet
candidates\footnote{The analysis was adapted from publicly available code that
was demonstrated to reproduce the same results as \citet{Burke:2015} by
\citet{Foreman-Mackey:2015a}.} and extrapolated to the center of the two
bins where we computed the occurrence rate.
At a period of 7~years and a radius of $0.2\,R_\mathrm{J}$, the extrapolated
occurrence is $0.73\pm0.28$ and at a radius of $0.6\,R_\mathrm{J}$, the
extrapolated rate is $0.15\pm0.05$.

@@

\begin{floattable}
\begin{deluxetable}{cccc}
\tabletypesize{\footnotesize}
\caption{The mass and semi-major axis estimates for the candidates from
Table~\ref{tab:catalog} \label{tab:masses}}
\include{masstab}
\tablenotetext{*}{The mass is estimated based on the measured radius using a
probabilistic mass--radius relation \citep{Chen:2016}.}
\end{deluxetable}
\end{floattable}

>>>>

For comparison, we repeated the analysis of \citet{Burke:2015} and fit a
double power-law occurrence rate to the short-period \kepler\ planet
candidates\footnote{The analysis was adapted from publicly available code that
was demonstrated to reproduce the same results as \citet{Burke:2015} by
\citet{Foreman-Mackey:2015a}.} and extrapolated to the center of the two
bins where we computed the occurrence rate.
At a period of 7~years and a radius of $0.2\,R_\mathrm{J}$, the extrapolated
occurrence is $0.73\pm0.28$ and at a radius of $0.6\,R_\mathrm{J}$, the
extrapolated rate is $0.15\pm0.05$.
These extrapolated values are qualitatively consistent with the rates listed
in Table~\ref{tab:occurrence} but we note that extrapolations and their
statistical uncertainties should not be taken too seriously.

@@

\begin{floattable}
\begin{deluxetable}{cccccccc}
\tabletypesize{\footnotesize}
\caption{The mass and semi-major axis estimates for the candidates from
Table~\ref{tab:catalog} \label{tab:masses}}
\include{masstab}
\tablecomments{The masses and radial velocity amplitudes are estimated based
on the measured radius using a probabilistic mass--radius relation
\citep{Chen:2016}.}
\end{deluxetable}
\end{floattable}
